### 2014-10-30 thesis/appendix/pt-corr-threshold-features.tex
All results are complete and tabulated nicely!

\begin{table}[htbp]
\caption{}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Pearson Correlation - Discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 13 & 92.86\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus, AdmissionDay, Age, AdmissionMonth \\ \hline
0.01 & 13 & 92.86\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus, AdmissionDay, Age, AdmissionMonth \\ \hline
0.05 & 12 & 85.71\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus, AdmissionDay, Age \\ \hline
0.1 & 10 & 71.43\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus \\ \hline
0.125 & 7 & 50.00\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex \\ \hline
0.15 & 6 & 42.86\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure \\ \hline
0.2 & 4 & 28.57\% & EpisodeType, MainDiagnosis, Education, InpatientService \\ \hline
0.3 & 1 & 7.14\% & EpisodeType \\ \hline
0.5 & 1 & 7.14\% & EpisodeType \\ \hline
0.75 & 1 & 7.14\% & EpisodeType \\ \hline
\end{tabular}}
\end{table}

\begin{table}[htbp]
\caption{}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{11cm}|}
\hline
\multicolumn{ 4}{|c|}{Pearson Correlation - No discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 14 & 100.00\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus, AdmissionDay, Age, prev\_adm, AdmissionMonth \\ \hline
0.01 & 14 & 100.00\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus, AdmissionDay, Age, prev\_adm, AdmissionMonth \\ \hline
0.05 & 12 & 85.71\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus, AdmissionDay, Age \\ \hline
0.1 & 10 & 71.43\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus \\ \hline
0.125 & 7 & 50.00\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex \\ \hline
0.15 & 6 & 42.86\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure \\ \hline
0.2 & 4 & 28.57\% & EpisodeType, MainDiagnosis, Education, InpatientService \\ \hline
0.3 & 1 & 7.14\% & EpisodeType \\ \hline
0.5 & 1 & 7.14\% & EpisodeType \\ \hline
0.75 & 1 & 7.14\% & EpisodeType \\ \hline
\end{tabular}}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Features selected from the discretised general hospital data set using varying thresholds of Pearson's correlation coefficient. Features shown are in order from highest to lowest correlation with the class.}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Pearson Correlation - Discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 13 & 92.86\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus, AdmissionDay, Age, AdmissionMonth \\ \hline
0.01 & 13 & 92.86\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus, AdmissionDay, Age, AdmissionMonth \\ \hline
0.05 & 12 & 85.71\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus, AdmissionDay, Age \\ \hline
0.1 & 10 & 71.43\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus \\ \hline
0.125 & 7 & 50.00\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex \\ \hline
0.15 & 6 & 42.86\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure \\ \hline
0.2 & 4 & 28.57\% & EpisodeType, MainDiagnosis, Education, InpatientService \\ \hline
0.3 & 1 & 7.14\% & EpisodeType \\ \hline
0.5 & 1 & 7.14\% & EpisodeType \\ \hline
0.75 & 1 & 7.14\% & EpisodeType \\ \hline
\end{tabular}}
\end{table}

\begin{table}[htbp]
\caption{Features selected from the non-discretised general hospital data set using varying thresholds of Pearson's correlation coefficient. Features shown are in order from highest to lowest correlation with the class.}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{11cm}|}
\hline
\multicolumn{ 4}{|c|}{Pearson Correlation - No discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 14 & 100.00\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus, AdmissionDay, Age, prev\_adm, AdmissionMonth \\ \hline
0.01 & 14 & 100.00\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus, AdmissionDay, Age, prev\_adm, AdmissionMonth \\ \hline
0.05 & 12 & 85.71\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus, AdmissionDay, Age \\ \hline
0.1 & 10 & 71.43\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex, MedicalSpecialty, AdmissionHour, MaritalStatus \\ \hline
0.125 & 7 & 50.00\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure, Sex \\ \hline
0.15 & 6 & 42.86\% & EpisodeType, MainDiagnosis, Education, InpatientService, OriginEpisodeType, MainProcedure \\ \hline
0.2 & 4 & 28.57\% & EpisodeType, MainDiagnosis, Education, InpatientService \\ \hline
0.3 & 1 & 7.14\% & EpisodeType \\ \hline
0.5 & 1 & 7.14\% & EpisodeType \\ \hline
0.75 & 1 & 7.14\% & EpisodeType \\ \hline
\end{tabular}}
\end{table}

### 2014-10-30 thesis/appendix/pt-ig-threshold-features.tex
All results are complete and tabulated nicely!

\begin{table}[htbp]
\caption{}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Information Gain - Discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 13 & 92.86\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex, AdmissionMonth \\ \hline
0.001 & 13 & 92.86\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex, AdmissionMonth \\ \hline
0.005 & 12 & 85.71\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex \\ \hline
0.01 & 12 & 85.71\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex \\ \hline
0.05 & 8 & 57.14\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour \\ \hline
0.1 & 7 & 50.00\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education \\ \hline
0.15 & 5 & 35.71\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty \\ \hline
0.2 & 3 & 21.43\% & EpisodeType, InpatientService, MainDiagnosis \\ \hline
0.3 & 2 & 14.29\% & EpisodeType, InpatientService \\ \hline
0.5 & 0 & 0.00\% &  \\ \hline
\end{tabular}}
\end{table}

\begin{table}[htbp]
\caption{}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Information Gain - No discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 14 & 100.00\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex, AdmissionMonth, prev\_adm \\ \hline
0.001 & 14 & 100.00\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex, AdmissionMonth, prev\_adm \\ \hline
0.005 & 12 & 85.71\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex \\ \hline
0.01 & 12 & 85.71\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex \\ \hline
0.05 & 8 & 57.14\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour \\ \hline
0.1 & 7 & 50.00\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education \\ \hline
0.15 & 5 & 35.71\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty \\ \hline
0.2 & 3 & 21.43\% & EpisodeType, InpatientService, MainDiagnosis \\ \hline
0.3 & 2 & 14.29\% & EpisodeType, InpatientService \\ \hline
0.5 & 0 & 0.00\% &  \\ \hline
\end{tabular}}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Features selected from the discretised general hospital data set at varying thresholds of information gain. Features shown are in order from highest to lowest information gain.}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Information Gain - Discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 13 & 92.86\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex, AdmissionMonth \\ \hline
0.001 & 13 & 92.86\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex, AdmissionMonth \\ \hline
0.005 & 12 & 85.71\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex \\ \hline
0.01 & 12 & 85.71\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex \\ \hline
0.05 & 8 & 57.14\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour \\ \hline
0.1 & 7 & 50.00\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education \\ \hline
0.15 & 5 & 35.71\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty \\ \hline
0.2 & 3 & 21.43\% & EpisodeType, InpatientService, MainDiagnosis \\ \hline
0.3 & 2 & 14.29\% & EpisodeType, InpatientService \\ \hline
0.5 & 0 & 0.00\% & - \\ \hline
\end{tabular}}
\end{table}

\begin{table}[htbp]
\caption{Features selected from the non-discretised general hospital data set at varying thresholds of information gain. Features shown are in order from highest to lowest information gain.}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Information Gain - No discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
0 & 14 & 100.00\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex, AdmissionMonth, prev\_adm \\ \hline
0.001 & 14 & 100.00\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex, AdmissionMonth, prev\_adm \\ \hline
0.005 & 12 & 85.71\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex \\ \hline
0.01 & 12 & 85.71\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour, AdmissionDay, MaritalStatus, Age, Sex \\ \hline
0.05 & 8 & 57.14\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education, AdmissionHour \\ \hline
0.1 & 7 & 50.00\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty, MainProcedure, Education \\ \hline
0.15 & 5 & 35.71\% & EpisodeType, InpatientService, MainDiagnosis, OriginEpisodeType, MedicalSpecialty \\ \hline
0.2 & 3 & 21.43\% & EpisodeType, InpatientService, MainDiagnosis \\ \hline
0.3 & 2 & 14.29\% & EpisodeType, InpatientService \\ \hline
0.5 & 0 & 0.00\% & - \\ \hline
\end{tabular}}
\end{table}

### 2014-10-30 thesis/appendix/pt-nothreshold-features.tex
All results are complete and tabulated nicely!

\begin{table}[h]
\caption{}
\begin{tabular}{|l|r|r|p{8.5cm}|}
\hline
\multicolumn{ 4}{|c|}{No Discretisation} \\ \hline
Method & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
CFS & 2 & 14.29\% & Episode Type, Main Diagnosis \\ \hline
C4.5 Wrapper & 4 & 28.57\% & Education, Episode Type, Inpatient Service, Main Diagnosis \\ \hline
\end{tabular}
\vspace{1cm}
\vfill
\begin{tabular}{|l|r|r|p{8.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Discretisation} \\ \hline
Method & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
CFS & 2 & 14.29\% & Episode Type, Main Diagnosis \\ \hline
C4.5 Wrapper & 4 & 28.57\% & Education, Episode Type, Inpatient Service, Main Diagnosis \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Features selected using automatic methods which select the best subset and do not require a threshold (CFS and C4.5 wrapper). Features are not ranked with these feature selectors. The same features are selected by each method regardless of discretisation or not.}
\begin{tabular}{|l|r|r|p{8.5cm}|}
\hline
\multicolumn{ 4}{|c|}{Discretisation/No Discretisation} \\ \hline
Method & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
CFS & 2 & 14.29\% & Episode Type, Main Diagnosis \\ \hline
C4.5 Wrapper & 4 & 28.57\% & Education, EpisodeType, InpatientService, MainDiagnosis \\ \hline
\end{tabular}
\end{table}

### 2014-10-30 thesis/appendix/pt-oner-threshold-features.tex
All results are complete and tabulated nicely!

\begin{table}[htbp]
\caption{}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{1R Accuracy - Discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
66.905 & 14 & 100.00\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure, AdmissionHour, Age, MaritalStatus, Education, prev\_adm, AdmissionDay, AdmissionMonth, Sex \\ \hline
67.905 & 14 & 100.00\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure, AdmissionHour, Age, MaritalStatus, Education, prev\_adm, AdmissionDay, AdmissionMonth, Sex \\ \hline
68.905 & 14 & 100.00\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure, AdmissionHour, Age, MaritalStatus, Education, prev\_adm, AdmissionDay, AdmissionMonth, Sex \\ \hline
69.905 & 14 & 100.00\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure, AdmissionHour, Age, MaritalStatus, Education, prev\_adm, AdmissionDay, AdmissionMonth, Sex \\ \hline
71.905 & 14 & 100.00\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure, AdmissionHour, Age, MaritalStatus, Education, prev\_adm, AdmissionDay, AdmissionMonth, Sex \\ \hline
74.405 & 14 & 100.00\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure, AdmissionHour, Age, MaritalStatus, Education, prev\_adm, AdmissionDay, AdmissionMonth, Sex \\ \hline
76.905 & 6 & 42.86\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure \\ \hline
81.905 & 3 & 21.43\% & EpisodeType, InpatientService, OriginEpisodeType \\ \hline
86.905 & 2 & 14.29\% & EpisodeType, InpatientService \\ \hline
96.905 & 0 & 0.00\% &  \\ \hline
\end{tabular}}
\end{table}

>>>>

\begin{table}[htbp]
\caption{Features selected from the general hospital data set using varying accuracy thresholds for the 1R feature selector. Features are shown in ranked order, from highest to lowest accuracy. The same features are selected regardless of discretisation.}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|r|r|r|p{9.5cm}|}
\hline
\multicolumn{ 4}{|c|}{1R Accuracy - Discretisation/No Discretisation} \\ \hline
\multicolumn{1}{|l|}{Threshold} & \multicolumn{1}{l|}{Num selected} & \multicolumn{1}{l|}{\% of total} & Features \\ \hline
66.905 & 14 & 100.00\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure, AdmissionHour, Age, MaritalStatus, Education, prev\_adm, AdmissionDay, AdmissionMonth, Sex \\ \hline
67.905 & 14 & 100.00\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure, AdmissionHour, Age, MaritalStatus, Education, prev\_adm, AdmissionDay, AdmissionMonth, Sex \\ \hline
68.905 & 14 & 100.00\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure, AdmissionHour, Age, MaritalStatus, Education, prev\_adm, AdmissionDay, AdmissionMonth, Sex \\ \hline
69.905 & 14 & 100.00\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure, AdmissionHour, Age, MaritalStatus, Education, prev\_adm, AdmissionDay, AdmissionMonth, Sex \\ \hline
71.905 & 14 & 100.00\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure, AdmissionHour, Age, MaritalStatus, Education, prev\_adm, AdmissionDay, AdmissionMonth, Sex \\ \hline
74.405 & 14 & 100.00\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure, AdmissionHour, Age, MaritalStatus, Education, prev\_adm, AdmissionDay, AdmissionMonth, Sex \\ \hline
76.905 & 6 & 42.86\% & EpisodeType, InpatientService, OriginEpisodeType, MedicalSpecialty, MainDiagnosis, MainProcedure \\ \hline
81.905 & 3 & 21.43\% & EpisodeType, InpatientService, OriginEpisodeType \\ \hline
86.905 & 2 & 14.29\% & EpisodeType, InpatientService \\ \hline
96.905 & 0 & 0.00\% & - \\ \hline
\end{tabular}}
\end{table}
